dbRDA analysis

### 2017-04-27 doc/RMD/RDA-analysis.Rmd
add ANOVA

@@

```{r resultplot, fig.width = 5, fig.height = 5}
cap11cc
cap11cc$anova
set.seed(99)
plot_dbrda(cap11cc) + 
  theme_classic(base_size = 16, base_family = "Helvetica") + 
  theme(axis.text = element_text(color = "black")) +
  theme(aspect.ratio = 1)
FILE <- file.path(PROJHOME, "results", "figures", "publication", "Figure7Z.svg")
ggsave(filename = FILE, width = 88, height = 88, units = "mm", scale = 1.5)
cap16cc
cap16cc$anova
plot_dbrda(cap16cc) +
  theme_classic(base_size = 16, base_family = "Helvetica") + 
  theme(axis.text = element_text(color = "black")) +
  theme(aspect.ratio = 1)
```

>>>>

# ANOVA

The results of our modeling and the marginal effects for each parameter on the
model itself.

```{r}
cap11cc
cap11cc$anova
cap16cc
cap16cc$anova
```

We can test the effects of how much of the model explains the variance

```{r total_anova, cache = TRUE}
anova(cap11cc)
anova(cap16cc)
```

We can also see the marginal effects with `by = "margin"`

```{r marginal_anova, cache = TRUE}
anova(cap11cc, by = "margin")
anova(cap16cc, by = "margin")
```

@@

```{r resultplot, fig.width = 5, fig.height = 5}
set.seed(99)
plot_dbrda(cap11cc) + 
  theme_classic(base_size = 16, base_family = "Helvetica") + 
  theme(axis.text = element_text(color = "black")) +
  theme(aspect.ratio = 1)
FILE <- file.path(PROJHOME, "results", "figures", "publication", "Figure7Z.svg")
ggsave(filename = FILE, width = 88, height = 88, units = "mm", scale = 1.5)
plot_dbrda(cap16cc) +
  theme_classic(base_size = 16, base_family = "Helvetica") + 
  theme(axis.text = element_text(color = "black")) +
  theme(aspect.ratio = 1)
```
